---
title: "scplots Tutorial"
#output: github_document
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    highlight: monochrome
    number_sections: no
    theme: flatly
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: true
      scroll_highlight: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(scplots)
```

## Dimensionality Reduction
### sc_dimred
#### Plotting function to visualize a scatter plot of dimensionality reduction (t-SNE, UMAP, PCA) results that highlight cells based on a phenotypic assignment.

```{r sc_dimred, results='asis', echo=TRUE, fig.height=6, fig.width=6, warning=FALSE, message=TRUE}
cat("Hey Hey")
plot(1:10,1:10)
```


### sc_dimred_express
#### Plotting function to visualize a scatter plot of dimensionality reduction (t-SNE, UMAP, PCA) results that highlight cells based on a phenotypic assignment.

```{r sc_dimred_express, results='asis', echo=TRUE, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}
cat("Hey Hey")
plot(1:10,1:10)
```


## Heatmap
### sc_heatmap
#### Plotting function to visualize a scatter plot of dimensionality reduction (t-SNE, UMAP, PCA) results that highlight cells based on a phenotypic assignment.

```{r sc_heatmap, results='asis', echo=TRUE, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}
cat("Hey Hey")
plot(1:10,1:10)
```


## Table
### sc_table
#### For plotting a table

```{r sc_table, results='asis', echo=TRUE, fig.height=6, fig.width=6, warning=FALSE, message=FALSE, dev="png"}
cat("Hey Hey")
plot(1:10,1:10)
```
